One-armed spirals in locally isothermal, radially structured self-gravitating discs

### 2014-11-16 paper/results_3d.tex
updating 3d results

\begin{figure}
  \begin{center}
    \subfigure[ZEUS-MP]{
      \includegraphics[scale=0.382]{figures/polarxy_dens015_z0}
      \includegraphics[scale=0.382,clip=true,trim=2.24cm 0cm 0cm
      0cm]{figures/polarxy_dens015_zmax}  
    }
    \subfigure[PLUTO]{
      \includegraphics[scale=0.382]{figures/pdisk_020_z0}
      \includegraphics[scale=0.382,clip=true,trim=2.24cm 0cm 0cm
      0cm]{figures/pdisk_020_zmax}
    }
  \end{center}
  \caption{Three-dimensional simulations using the ZEUS-MP (top) and 
    PLUTO (bottom) codes. The non-axisymmetric density at the midplane (left) and
    two scale-heights above the midplane (right) is shown. Here $\psi
    \equiv \pi/2 - \theta$ is the angular height  
    from the midplane.\label{3d_prelim}}   
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.47,clip=true,trim=0cm 0.79cm 0cm 0cm]{figures/pdisk_rz_020_sg.ps}
  \includegraphics[scale=0.47,clip=true,trim=0cm 0cm 0cm 0.64cm]{figures/pdisk_rz_020_nsg.ps}
  \caption{Non-axisymmetric density in the meridional plane from the
    PLUTO simulation. The slices are taken at the azimuth of   
    $\mathrm{max}[\Delta\rho(r,\pi/2,\phi)]$. Arrows correspond to the vector 
    $(v_r/R_0,-v_\theta/rh\sin^2{\theta})$. The top (bottom) panel corresponds
    to the inner (outer) portions of the disc. 
    \label{3d_rz}} 
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \subfigure[ZEUS-MP]{
      \includegraphics[scale=0.305,clip=true,trim=0cm 0cm 0cm 0cm]{figures/polarxy2_dens015_z0}  
      \includegraphics[scale=0.305,clip=true,trim=0.8cm 0cm 0cm
      0cm]{figures/polarxy2_dens015_zmax}  
    }
    \subfigure[PLUTO]{
      \includegraphics[scale=0.305,clip=true,trim=0cm 0cm 0cm 0cm]{figures/pdiskxy_023_z0}
      \includegraphics[scale=0.305,clip=true,trim=0.8cm 0cm 0cm
      0cm]{figures/pdiskxy_023_zmax}
    }
  \end{center}
  \caption{Three-dimensional simulations using the ZEUS-MP (top) and 
    PLUTO (bottom) codes. The $m=1$ density component $\Delta\rho_1$ at the midplane (left) and
    two scale-heights above the midplane (right) is shown. Here $\psi
    \equiv \pi/2 - \theta$ is the angular height  
    from the midplane. \label{3d_prelim}}   
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.47,clip=true,trim=0cm 0.79cm 0cm
  0cm]{figures/pdisk_rz_023_sg.ps}  
  \includegraphics[scale=0.47,clip=true,trim=0cm 0cm 0cm
  0.64cm]{figures/pdisk_rz_023_nsg.ps}  
  \caption{Vertical distribution of the $m=1$ density component in the meridional plane from the 
    PLUTO simulation. The slices are taken at the azimuth of   
    $\mathrm{max}[\Delta\rho_1(r,\pi/2,\phi)]$. Arrows correspond to the vector 
    $(v_r/R_0,-v_\theta/rh\sin^2{\theta})$. The top (bottom) panel corresponds
    to the inner (outer) portions of the disc. 
    \label{3d_rz}} 
\end{figure}
